### 2021-02-24 notes/notes.tex
Added RandomVariable. Not much else...

Spontaneous recovery. In an A-B-error_clamp paradigm, in which during B the
opposite adaptation to A is learned, at the beginning of the error-clamp phase
(after B) participants seem to quickly gravitate towards A (thinking that A is
now active?). This would be displayed by the model via the state inference, as
now the visual cue and the observed dynamics point to different contexts. In
time, updating $p(context | visual cue)$ will lead to spontaneous recovery.

@@

\begin{chapter}{Testing the model in \ref{subsec:proposal}}
In this section, I propose a simulated task in which the prowess of the model proposed in \ref{subsec:proposal} is put to the test. I additionally present simulation results and some writeup. Basically a mini-paper on this model.

>>>>

Spontaneous recovery. In an A-B-error\_clamp paradigm, in which during B the
opposite adaptation to A is learned, at the beginning of the error-clamp phase
(after B) participants seem to quickly gravitate towards A (thinking that A is
now active?). This would be displayed by the model via the state inference, as
now the visual cue and the observed dynamics point to different contexts. In
time, updating $p(context | visual cue)$ will lead to spontaneous recovery.

@@

\begin{chapter}{Implementing the adaptation model}
In this section, I propose a simulated task in which the prowess of the model proposed in \ref{subsec:proposal} is put to the test. I additionally present simulation results and some writeup. Basically a mini-paper on this model.
